Urban Heat Risk Mapping Using Multiple Point Patterns in Houston, Texas

### 2016-11-11 reviewer_response.tex

\documentclass{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage{dsfont}
\usepackage{bm}
\usepackage{csquotes}

\begin{document}
\section{Response to Comments From Reviewer 1}
\subsection{I really feel given the nature of this paper (it is not the definitive guide to heat and health in Houston) that it needs to be fully capable of reproducibility.   I therefore don't feel the part of the algorithm set out in section 2.4 is sufficient.   For example I had to read to find details for $\boldsymbol{\alpha}_p$ etc., some of the other comments (the posterior is fully known) were a little glib.   I think the entire sampler could be set out in the text, but if not an appendix could be used.   Links to code would also be helpful (I appreciate there are confidentiality issues with some of the data).}

Valid point. We rearranged the paper to put all of the information relevant to the algorithm in 2.4 together in the same section, making it easier to find details about how the model was fit. We also provided additional description to clarify what was meant by our comments such as ``the posterior is fully known.''

\subsection{I don't think the comments on convergence are adequate.   On page 13 line 10; how does MCSE alone provide evidence of convergence?   I think more is needed.}
We have attached traceplots to this document and can include them in the supplementary materials for the paper if desired. Additionally, we added further detail about how MCSE provides evidence of convergence on page 14 with the following statement:

\begin{displayquote}
In order to assess convergence, we examined traceplots for each of the parameters and used Monte Carlo standard error (MCSE). Jones et. al. (2006) calculate MCSE by dividing the chains into batches and using each batch mean to calculate variance between batches. Small MCSE values occur only when the variance between batches is low (i.e., each batch is approximately equal), thereby providing evidence of convergence.
\end{displayquote}

\end{document}

### 2016-11-11 jrssc-mpp.tex
Further clarification of algorithm in section 2.4 and detail about MCSE. Also added reviewer response file

 \textcolor{red}{The posterior densities for the rest of the parameters are unknown and so we obtain draws from the posterior using a Metropolis within Gibbs sampler of the following form:
\begin{enumerate}
  \item \label{draws2} For $p = 1, \dots, P$, sample $\sigma^2_p \sim \mathcal{IG}(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}\boldsymbol\phi^{\star\prime}\mathbf{M}_p^{-1}\boldsymbol\phi^\star)$;%[ \sigma^2_p | \boldsymbol{\phi}^\star_p, \mathbf{M}_p]$;
  \item \label{drawphi} For $p = 1, \dots, P$, sample $\boldsymbol\phi^\star_p \sim [ \boldsymbol\phi^\star_p | \sigma^2_p, \mathbf{M}_p ]$;
  \item \label{drawsmu} Sample $\sigma^2_\mu \sim \mathcal{IG}(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta)^\prime\mathbf{M}^{-1}_\mu(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta));$%[ \sigma^2_\mu | \boldsymbol{\mu}, \boldsymbol{\beta}, \mathbf{M}_\mu ]$;
  \item \label{drawmu} Sample $\boldsymbol{\mu} \sim [ \boldsymbol{\mu} | \{\boldsymbol{\phi}^\star_p\}, 
    \{\sigma^2_p\}, \{\mathbf{M}_p\}, \sigma^2_\mu, \mathbf{M}_\mu, \boldsymbol{\beta} ]$; and
  \item \label{drawbeta} Sample $\boldsymbol{\beta} \sim \mathcal{N}(\sigma_\mu^{-2}\Sigma^{\star}\mathbf{X}^\prime\mathbf{M}_\mu^{-1}\boldsymbol\mu, \Sigma^\star)$, where $\Sigma^\star = \left[\frac{1}{50}I_Q + \frac{1}{\sigma^2_\mu}\mathbf{X}^\prime \mathbf{M}_\mu^{-1}\mathbf{X}\right]^{-1}$.%[ \boldsymbol{\beta} | \boldsymbol{\mu}, \sigma^2_\mu, \mathbf{M}_\mu ]$.
\end{enumerate}}

Note that for steps \ref{draws2}, \ref{drawsmu}, and \ref{drawbeta} we have the complete conditional distributions, but that \ref{drawphi} and \ref{drawmu} require a Metropolis-Hastings (MH) update. Using a sampler of this design, 10000 draws were taken from the posterior distributions for each of these parameters, after a burn-in of 10000. In order to assess convergence, we used Monte Carlo standard error (MCSE). MCSE provides evidence of convergence by Monte Carlo standard error (MCSE) was calculated for each chain and provided evidence that all of them converged \citep{Flegal2015}.

@@

\begin{figure}
  \centering
  \begin{minipage}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{./imgs/delta_911.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{./imgs/delta_mortality.pdf}
  \end{minipage}
  \caption{Posterior density plots for $\delta_{911}$ and $\delta_{Mort}$.}
  \label{kde}
\end{figure}

>>>>

 \textcolor{red}{The posterior densities for the rest of the parameters are unknown and so we obtain draws from the posterior using a Metropolis within Gibbs sampler of the following form:
\begin{enumerate}
  \item \label{draws2} For $p = 1, \dots, P$, sample $\sigma^2_p \sim \left[ \sigma^2_p | \boldsymbol{\phi}^\star_p, \mathbf{M}_p\right]$;
  \item \label{drawphi} For $p = 1, \dots, P$, sample $\boldsymbol\phi^\star_p \sim \left[ \boldsymbol\phi^\star_p | \sigma^2_p, \mathbf{M}_p \right]$;
  \item \label{drawsmu} Sample $\sigma^2_\mu \sim \left[ \sigma^2_\mu | \boldsymbol{\mu}, \boldsymbol{\beta}, \mathbf{M}_\mu \right]$;
  \item \label{drawmu} Sample $\boldsymbol{\mu} \sim \left[ \boldsymbol{\mu} | \{\boldsymbol{\phi}^\star_p\}, 
    \{\sigma^2_p\}, \{\mathbf{M}_p\}, \sigma^2_\mu, \mathbf{M}_\mu, \boldsymbol{\beta} \right]$; and
  \item \label{drawbeta} Sample $\boldsymbol{\beta} \sim \left[ \boldsymbol{\beta} | \boldsymbol{\mu}, \sigma^2_\mu, \mathbf{M}_\mu \right]$.
\end{enumerate}}

\textcolor{red}{
We use the notation $\left[\theta | \psi_1, \dots, \psi_k \right]$ to represent the complete conditional for the parameter $\theta$ dependent on parameters $\psi_1, \dots, \psi_k$. Note that for steps \ref{draws2}, \ref{drawsmu}, and \ref{drawbeta} the complete conditional distributions are}
\begin{equation}
\sigma^2_p \sim \mathcal{IG}\left(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}\boldsymbol\phi_p^{\star\prime}\mathbf{M}_p^{-1}\boldsymbol\phi_p^\star\right),
\end{equation}
\begin{equation}
\sigma^2_\mu \sim \mathcal{IG}\left(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta)^\prime\mathbf{M}^{-1}_\mu(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta)\right), \text{ and }
\end{equation}
\begin{equation}
\boldsymbol{\beta} \sim \mathcal{N}\left(\sigma_\mu^{-2}\Sigma^{\star}\mathbf{X}^\prime\mathbf{M}_\mu^{-1}\boldsymbol\mu, \Sigma^\star)\right), 
\end{equation}
where $M_p$ and $M_\mu$ are defined as in \eqref{phiprior} and \eqref{mu} and where $\Sigma^\star = \left[\frac{1}{50}I_Q + \frac{1}{\sigma^2_\mu}\mathbf{X}^\prime \mathbf{M}_\mu^{-1}\mathbf{X}\right]^{-1}$. 
\textcolor{red}{
Because these belong to known families they can be drawn from directly using a Gibbs update, but the complete conditional distributions in steps \ref{drawphi} and \ref{drawmu} are not known and require a Metropolis-Hastings (MH) update. Using a sampler of this design, 10000 draws were taken from the posterior distributions for each of these parameters, after a burn-in of 10000.\footnote{R code used to implement this algorithm is provided in the supplementary materials.m} In order to assess convergence, we examined traceplots for each of the parameters and used Monte Carlo standard error (MCSE). \cite{Jones2006} calculate MCSE by dividing the chains into batches and using each batch mean to calculate variance between batches. Small MCSE values occur only when the variance between batches is low (i.e., each batch is approximately equal), thereby providing evidence of convergence. We calculated MCSE using the \texttt{mcmcse} package in R \citep{Flegal2015}, and the largest MCSE value for all of our parameters was XXXXX. Based on these MCSE values and visual inspection of the traceplots, we are satisfied that convergence was attained.}

%They essentially argue that having a low MCSE can only happen for converged chains.  The reason they can say this is because they use the batch means estimates to get at the MCSE.  By batch means, they break the whole chain into pieces (batches) then calculate the variance between batches.  The argument is that the variance between batches can only be small when each batch is approximately equal; hence the algorithm is "converged".

@@

\begin{figure}
  \centering
  \begin{minipage}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{./imgs/delta_911.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{./imgs/delta_mortality.pdf}
  \end{minipage}
  \caption{Posterior density plots for $\delta_{911}$ and $\delta_{Mort}$.}
  \label{fig:delta_kde}
\end{figure}
